---
title: "Using dplyr and Redshift"
author: "Michael Treadwell"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using dplyr and Redshift}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Amazon Redshift is based on PostgreSQL 8.0.2. For this reason, you can use `src_postgres` from the [dplyr package](https://cran.r-project.org/web/packages/dplyr/vignettes/databases.html) to connect to your Amazon Redshift cluster. However, because there are some important differences between Postgres and Redshift syntax, users can encounter some small yet annoying errors.

## The Postgres Problem

For example, if you've connected to a Redshift cluster using `src_postgres` and attempted to use `lag` then you've probably received this message `ERROR: Default parameter not be supported for window function lag`.

```{r, eval = FALSE}
library(dplyr)
library(RPostgreSQL)

pg <- src_postgres('dbname',
                   host = 'redshift.amazonaws.com',
                   port = '5439',
                   user = 'user',
                   password = 'password')

tbl(pg, 'tablename') %>%
  mutate(last_value = lag(value, order = 'date'))
```

## The Redshift Solution

The package redshyft introduces the function `src_redshift` which enables users to connect to a Redshift cluster and use the basic dplyr verbs without error.

```{r, eval = FALSE}
library(dplyr)
library(redshyft)

rs <- src_redshift('dbname',
                   host = 'redshift.amazonaws.com',
                   port = '5439',
                   user = 'user',
                   password = 'password')

tbl(rs, 'tablename') %>%
  mutate(last_value = lag(value, order = 'date'))
```
